---
title: "Biodiversity WTP Analysis - Summary Report"
date: "`r Sys.Date()`"
format: 
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    theme: cosmo
    embed-resources: true
    fig-width: 14
    fig-height: 18
params:
  scenarios:
    value:
      - baseline
  models:
    value:
      - Basic
  output_dir:
    value: "output/scenarios"
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(kableExtra)
library(RColorBrewer)
library(htmltools)

# Get parameters
scenarios <- params$scenarios
models <- params$models
output_dir <- params$output_dir

message("Scenarios: ", paste(scenarios, collapse = ", "))
message("Models: ", paste(models, collapse = ", "))
message("Output directory: ", output_dir)

# Verify scenario directories exist
for (scenario in scenarios) {
  scenario_dir <- file.path(output_dir, scenario)
  if (!dir.exists(scenario_dir)) {
    warning("Scenario directory not found: ", scenario_dir)
  }
}
```

# Overview

This report summarizes the Random Utility Model (RUM) analysis across **`r length(scenarios)` scenarios**: `r paste(scenarios, collapse = ", ")`.

---

# Voronoi Clusters

:::{.panel-tabset}

```{r voronoi-tabs, results='asis'}
for (scenario in scenarios) {
  figures_dir <- file.path("output", "scenarios", scenario, "figures")
  voronoi_files <- list.files(figures_dir, pattern = "^voronoi_map.*\\.png$", full.names = FALSE)
  cat('\n##', scenario, '\n\n')
  if (length(voronoi_files) == 0) {
    cat("Voronoi map not found for scenario:", scenario, "\n\n")
  } else {
    vf <- voronoi_files[1]
    rel_path <- file.path("output", "scenarios", scenario, "figures", vf)
    abs_path <- here::here(rel_path)
    if (file.exists(abs_path)) {
      cat('![](', rel_path, '){ width=100% }\n\n', sep = '')
    }
  }
}
```

:::

---

# Data Summary

```{r data-summary-combined}
# Load only data_summary_ER.csv for each scenario, with debug prints
summary_list <- list()
for (scenario in scenarios) {
  summary_path <- file.path(output_dir, scenario, "tables", "data_summary_basic_ER.csv")
  if (file.exists(summary_path)) {
    df <- read.csv(summary_path, stringsAsFactors = FALSE)
    # Add all variables used in WTP plots to the summary
    wtp_plot_vars <- c(
      "expected_richness", "migrant_richness", "resident_richness", "species_richness", "shannon_index", "simpson_index",
      "expected_richness_Winter", "expected_richness_Spring", "expected_richness_Summer", "expected_richness_Fall",
      "migrant_richness_Winter", "migrant_richness_Spring", "migrant_richness_Summer", "migrant_richness_Fall",
      "resident_richness_Winter", "resident_richness_Spring", "resident_richness_Summer", "resident_richness_Fall",
      "species_richness_Winter", "species_richness_Spring", "species_richness_Summer", "species_richness_Fall",
      "shannon_index_Winter", "shannon_index_Spring", "shannon_index_Summer", "shannon_index_Fall",
      "simpson_index_Winter", "simpson_index_Spring", "simpson_index_Summer", "simpson_index_Fall"
    )
    key_vars <- c("Sample Size", "Number of Trips", "Number of Users",
                  wtp_plot_vars,
                  "expected_congestion", "precip", 
                  "temp", "trees", "travel_cost_combined", "dist_to_pa_km")
    found_vars <- intersect(key_vars, df$variable)
    df_filtered <- df %>%
      filter(variable %in% key_vars) %>%
      select(variable, mean, sd)
    df_filtered <- df_filtered %>%
      mutate(
        formatted = ifelse(
          variable %in% c("Sample Size", "Number of Trips", "Number of Users"),
          format(round(mean, 0), big.mark = ",", scientific = FALSE),
          paste0(
            format(round(mean, 2), nsmall = 2),
            ifelse(!is.na(sd) & sd > 0, 
                   paste0(" (", format(round(sd, 2), nsmall = 2), ")"),
                   "")
          )
        )
      )
    summary_list[[scenario]] <- df_filtered %>%
      select(variable, formatted)
    names(summary_list[[scenario]])[2] <- scenario
  } else {
    cat("[DataSummary] NOT FOUND: ", summary_path)
  }
}

# Merge all scenarios
if (length(summary_list) > 0) {
  summary_combined <- Reduce(function(x, y) {
    full_join(x, y, by = "variable")
  }, summary_list)
  
  # Reorder rows
  var_order <- c(
    "Sample Size", "Number of Trips", "Number of Users",
    "expected_richness", "migrant_richness", "resident_richness", "shannon_index",  "simpson_index",
    "expected_richness_Winter", "expected_richness_Spring",   "expected_richness_Summer", "expected_richness_Fall",
    "migrant_richness_Winter", "migrant_richness_Spring", "migrant_richness_Summer",  "migrant_richness_Fall",
    "resident_richness_Winter", "resident_richness_Spring",   "resident_richness_Summer", "resident_richness_Fall",
    "shannon_index_Winter", "shannon_index_Spring", "shannon_index_Summer",   "shannon_index_Fall",
    "simpson_index_Winter", "simpson_index_Spring", "simpson_index_Summer",   "simpson_index_Fall",
    "expected_congestion", "precip", "temp", "trees", "travel_cost_combined",   "dist_to_pa_km"
  )
  
  summary_combined <- summary_combined %>%
    mutate(variable = factor(variable, levels = var_order)) %>%
    arrange(variable) %>%
    filter(!is.na(variable)) %>%   # drop anything not in var_order
    mutate(variable = as.character(variable))
  
  # Clean variable names for display
  summary_combined <- summary_combined %>%
    mutate(
      Variable = case_when(
        variable == "Sample Size" ~ "Sample Size",
        variable == "Number of Trips" ~ "Number of Trips",
        variable == "Number of Users" ~ "Number of Users",
        variable == "expected_richness" ~ "Expected Richness",
        variable == "expected_congestion" ~ "Expected Congestion",
        variable == "precip" ~ "Precipitation (mm)",
        variable == "temp" ~ "Temperature (°C)",
        variable == "trees" ~ "Tree Cover (%)",
        variable == "travel_cost_combined" ~ "Travel Cost (INR)",
        variable == "dist_to_pa_km" ~ "Distance to PA (km)",
          variable == "migrant_richness" ~ "Migrant Richness",
          variable == "resident_richness" ~ "Resident Richness",
          variable == "species_richness" ~ "Species Richness",
          variable == "shannon_index" ~ "Shannon Index",
          variable == "simpson_index" ~ "Simpson Index",
          variable == "expected_richness_Winter" ~ "Expected Richness (Winter)",
          variable == "expected_richness_Spring" ~ "Expected Richness (Spring)",
          variable == "expected_richness_Summer" ~ "Expected Richness (Summer)",
          variable == "expected_richness_Fall" ~ "Expected Richness (Fall)",
          variable == "migrant_richness_Winter" ~ "Migrant Richness (Winter)",
          variable == "migrant_richness_Spring" ~ "Migrant Richness (Spring)",
          variable == "migrant_richness_Summer" ~ "Migrant Richness (Summer)",
          variable == "migrant_richness_Fall" ~ "Migrant Richness (Fall)",
          variable == "resident_richness_Winter" ~ "Resident Richness (Winter)",
          variable == "resident_richness_Spring" ~ "Resident Richness (Spring)",
          variable == "resident_richness_Summer" ~ "Resident Richness (Summer)",
          variable == "resident_richness_Fall" ~ "Resident Richness (Fall)",
          variable == "species_richness_Winter" ~ "Species Richness (Winter)",
          variable == "species_richness_Spring" ~ "Species Richness (Spring)",
          variable == "species_richness_Summer" ~ "Species Richness (Summer)",
          variable == "species_richness_Fall" ~ "Species Richness (Fall)",
          variable == "shannon_index_Winter" ~ "Shannon Index (Winter)",
          variable == "shannon_index_Spring" ~ "Shannon Index (Spring)",
          variable == "shannon_index_Summer" ~ "Shannon Index (Summer)",
          variable == "shannon_index_Fall" ~ "Shannon Index (Fall)",
          variable == "simpson_index_Winter" ~ "Simpson Index (Winter)",
          variable == "simpson_index_Spring" ~ "Simpson Index (Spring)",
          variable == "simpson_index_Summer" ~ "Simpson Index (Summer)",
          variable == "simpson_index_Fall" ~ "Simpson Index (Fall)",
        TRUE ~ variable
      )
    ) %>%
    select(-variable) %>%
    select(Variable, everything())
  
  kable(summary_combined,
        align = c("l", rep("r", length(scenarios))),
        caption = "Summary Statistics Across Scenarios (Mean with SD in parentheses)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE) %>%
    row_spec(0, bold = TRUE) %>%
    row_spec(1:3, background = "#f0f0f0")
} else {
  cat("No summary data available")
}
```

# Definitions

### Species Richness Measures

**Expected Species Richness** is computed as the mean number of unique species 
observed across all checklists recorded at a site within a given time period. 
If expected richness cannot be computed directly for a group or time period, 
the pipeline uses the following fallback:

- If the previous week value is available, use that.
- If not, use the previous month value.
- If not, use the previous year-season value.
- If none are available, the value is marked as missing.

**Migrant Richness** and **Resident Richness** are computed analogously, 
restricted to species classified as migratory or resident, respectively.

### Diversity Indices

Diversity indices are computed at the checklist (trip) level using recorded observation counts. For checklists where counts were not recorded (entered as "X" in eBird), indices are set to missing. Unlike the richness measures above, no fallback imputation is applied.

**Shannon Index ($H$):**

The Shannon diversity index quantifies the entropy (uncertainty) in species composition:

$$
H = -\sum_{i=1}^S p_i \log p_i
$$

where $S$ is the number of species detected and 
$p_i = \frac{n_i}{\sum_{j=1}^S n_j}$ is the proportion of total observed individuals belonging to species $i$, based on recorded observation counts. Higher values indicate greater diversity and evenness across species.

**Gini-Simpson Index ($D$):**

The Gini-Simpson index measures the probability that two randomly selected 
individuals belong to *different* species:

$$
D = 1 - \sum_{i=1}^S p_i^2
$$

where $S$ is the number of species detected and 
$p_i = \frac{n_i}{\sum_{j=1}^S n_j}$ is the proportion of total observed  individuals belonging to species $i$, based on recorded observation counts.  Values range from 0 (no diversity) to 1 (maximum diversity).

---

# Willingness to Pay Estimates

```{r wtp-data-prep, echo=FALSE, message=FALSE}
models <- unique(models)

wtp_list <- list()
models <- c()
for (scenario in scenarios) {
  models_dir <- file.path(output_dir, scenario, "models")
  wtp_files <- list.files(models_dir, pattern = "^wtp_.*\\.rds$", full.names = TRUE)
  for (wtp_path in wtp_files) {
    model_name <- sub("^wtp_(.*)\\.rds$", "\\1", basename(wtp_path))
    if (file.exists(wtp_path)) {
      models <- c(models, model_name)
      tryCatch({
        wtp_obj <- readRDS(wtp_path)
        wtp_df <- NULL
        se_found <- FALSE
        # Handle summary.logitr objects (with coefTable)
        if (inherits(wtp_obj, "summary.logitr") && !is.null(wtp_obj$coefTable)) {
          coef_table <- wtp_obj$coefTable
          if ("Std. Error" %in% names(coef_table)) {
            se_values <- as.numeric(coef_table$`Std. Error`)
            se_found <- all(!is.na(se_values))
          } else {
            se_values <- rep(NA_real_, nrow(coef_table))
          }
          variable_names <- rownames(coef_table)
          wtp_df <- data.frame(
            variable = variable_names,
            estimate = as.numeric(coef_table$Estimate),
            se = se_values,
            scenario = scenario,
            model = model_name,
            stringsAsFactors = FALSE
          )
        } else if (is.data.frame(wtp_obj) && "Estimate" %in% names(wtp_obj)) {
          if (!is.null(rownames(wtp_obj)) && !all(rownames(wtp_obj) %in% as.character(1:nrow(wtp_obj)))) {
            variable_names <- rownames(wtp_obj)
          } else if ("variable" %in% names(wtp_obj)) {
            variable_names <- as.character(wtp_obj$variable)
          } else {
            variable_names <- paste0("V", seq_len(nrow(wtp_obj)))
          }
          if ("Std. Error" %in% names(wtp_obj)) {
            se_values <- as.numeric(wtp_obj[["Std. Error"]])
            se_found <- all(!is.na(se_values))
          } else {
            se_values <- rep(NA_real_, nrow(wtp_obj))
          }
          wtp_df <- data.frame(
            variable = variable_names,
            estimate = as.numeric(wtp_obj$Estimate),
            se = se_values,
            scenario = scenario,
            model = model_name,
            stringsAsFactors = FALSE
          )
        } else if (is.list(wtp_obj) && !is.null(wtp_obj$Estimate)) {
          wtp_df <- data.frame(
            variable = names(wtp_obj$Estimate),
            estimate = as.numeric(wtp_obj$Estimate),
            se = NA_real_,
            scenario = scenario,
            model = model_name,
            stringsAsFactors = FALSE
          )
        } else if (is.matrix(wtp_obj)) {
          if ("Std. Error" %in% colnames(wtp_obj)) {
            se_values <- as.numeric(wtp_obj[, "Std. Error"])
            se_found <- all(!is.na(se_values))
          } else {
            se_values <- rep(NA_real_, nrow(wtp_obj))
          }
          wtp_df <- data.frame(
            variable = rownames(wtp_obj),
            estimate = as.numeric(wtp_obj[, "Estimate"]),
            se = se_values,
            scenario = scenario,
            model = model_name,
            stringsAsFactors = FALSE
          )
        }
        # Throw error and print structure if SE not found
        if (!se_found) {
          cat("\n[ERROR] No standard errors found for scenario:", scenario, "model:", model_name, "\n")
          print(str(wtp_obj))
          stop("Standard errors missing in WTP object.")
        }
        if (!is.null(wtp_df)) {
          wtp_df <- wtp_df %>% filter(variable != "scalePar", !grepl("^sd_", variable))
          wtp_list[[paste(scenario, model_name, sep = "_")]] <- wtp_df
        }
      }, error = function(e) {
        cat("\n[ERROR] Failed to load WTP for scenario:", scenario, "model:", model_name, "\n")
        print(e)
      })
    }
  }
}
```

```{r wtp-prepare-plots}
if (length(wtp_list) > 0) {
  wtp_combined <- bind_rows(wtp_list)
  wtp_combined <- wtp_combined %>% mutate(variable = gsub("_dm$", "", variable))
  wtp_combined <- wtp_combined %>% mutate(
    ci_lower = estimate - 1.96 * se,
    ci_upper = estimate + 1.96 * se
  )

  # ER overall + migrant richness + index vars
  er_vars <- c("expected_richness", "migrant_richness", "resident_richness",  "shannon_index", "simpson_index")
  er_labels <- c(
    "expected_richness" = "Expected Richness (Overall)",
    "migrant_richness"  = "Migrant Richness (Overall)",
    "resident_richness" = "Resident Richness (Overall)",
    "shannon_index"     = "Shannon Index (Overall)",
    "simpson_index"     = "Simpson Index (Overall)"
  )
  wtp_er <- wtp_combined %>% filter(variable %in% er_vars) %>%
    mutate(
      variable_clean = er_labels[variable],
      variable_clean = factor(variable_clean, levels = er_labels[er_vars])
    )

  # ERseason + migrant + index seasonal
  erseason_vars <- c(
    "expected_richness_Winter", "expected_richness_Spring",   "expected_richness_Summer", "expected_richness_Fall",
    "migrant_richness_Winter",  "migrant_richness_Spring",    "migrant_richness_Summer",  "migrant_richness_Fall",
    "resident_richness_Winter", "resident_richness_Spring",   "resident_richness_Summer", "resident_richness_Fall",
    "shannon_index_Winter",     "shannon_index_Spring",       "shannon_index_Summer",     "shannon_index_Fall",
    "simpson_index_Winter",     "simpson_index_Spring",       "simpson_index_Summer",     "simpson_index_Fall"
  )
  erseason_labels <- c(
    "expected_richness_Winter" = "Expected Richness (Winter)",
    "expected_richness_Spring" = "Expected Richness (Spring)",
    "expected_richness_Summer" = "Expected Richness (Summer)",
    "expected_richness_Fall"   = "Expected Richness (Fall)",
    "migrant_richness_Winter"  = "Migrant Richness (Winter)",
    "migrant_richness_Spring"  = "Migrant Richness (Spring)",
    "migrant_richness_Summer"  = "Migrant Richness (Summer)",
    "migrant_richness_Fall"    = "Migrant Richness (Fall)",
    "resident_richness_Winter" = "Resident Richness (Winter)",
    "resident_richness_Spring" = "Resident Richness (Spring)",
    "resident_richness_Summer" = "Resident Richness (Summer)",
    "resident_richness_Fall"   = "Resident Richness (Fall)",
    "shannon_index_Winter"     = "Shannon Index (Winter)",
    "shannon_index_Spring"     = "Shannon Index (Spring)",
    "shannon_index_Summer"     = "Shannon Index (Summer)",
    "shannon_index_Fall"       = "Shannon Index (Fall)",
    "simpson_index_Winter"     = "Simpson Index (Winter)",
    "simpson_index_Spring"     = "Simpson Index (Spring)",
    "simpson_index_Summer"     = "Simpson Index (Summer)",
    "simpson_index_Fall"       = "Simpson Index (Fall)"
  )
  wtp_erseason <- wtp_combined %>% filter(variable %in% erseason_vars) %>%
    mutate(
      variable_clean = erseason_labels[variable],
      variable_clean = factor(variable_clean, levels = erseason_labels[erseason_vars])
    )
  
  # Biodiversity indices overall
  index_vars <- c("resident_richness", "shannon_index", "simpson_index")
  index_labels <- c(
    "resident_richness" = "Resident Richness",
    "shannon_index"     = "Shannon Index",
    "simpson_index"     = "Simpson Index"
  )
  wtp_index <- wtp_combined %>% filter(variable %in% index_vars) %>%
    mutate(
      variable_clean = index_labels[variable],
      variable_clean = factor(variable_clean, levels = index_labels[index_vars])
    )

  # Biodiversity indices seasonal
  index_season_vars <- c(
    "resident_richness_Winter", "resident_richness_Spring",   "resident_richness_Summer", "resident_richness_Fall",
    "shannon_index_Winter", "shannon_index_Spring", "shannon_index_Summer",   "shannon_index_Fall",
    "simpson_index_Winter", "simpson_index_Spring", "simpson_index_Summer",   "simpson_index_Fall"
  )
  index_season_labels <- c(
    "resident_richness_Winter" = "Resident Richness (Winter)",
    "resident_richness_Spring" = "Resident Richness (Spring)",
    "resident_richness_Summer" = "Resident Richness (Summer)",
    "resident_richness_Fall"   = "Resident Richness (Fall)",
    "shannon_index_Winter"     = "Shannon Index (Winter)",
    "shannon_index_Spring"     = "Shannon Index (Spring)",
    "shannon_index_Summer"     = "Shannon Index (Summer)",
    "shannon_index_Fall"       = "Shannon Index (Fall)",
    "simpson_index_Winter"     = "Simpson Index (Winter)",
    "simpson_index_Spring"     = "Simpson Index (Spring)",
    "simpson_index_Summer"     = "Simpson Index (Summer)",
    "simpson_index_Fall"       = "Simpson Index (Fall)"
  )
  wtp_index_seasonal <- wtp_combined %>% filter(variable %in% index_season_vars) %>%
    mutate(
      variable_clean = index_season_labels[variable],
      variable_clean = factor(variable_clean, levels = index_season_labels  [index_season_vars])
  )

  # Color map
  scenario_names <- unique(wtp_combined$scenario)
  n_scenarios <- length(scenario_names)
  if (n_scenarios <= 8) {
    palette <- RColorBrewer::brewer.pal(n_scenarios, "Set1")
  } else {
    palette <- colorRampPalette(RColorBrewer::brewer.pal(8, "Set1"))(n_scenarios)
  }
  scenario_color_map <- setNames(palette, scenario_names)

  # Plot ER overall
  p_er <- ggplot(wtp_er, aes(x = scenario, y = estimate, color = scenario, group = scenario)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                  width = 0.3, linewidth = 0.9, position = position_dodge(width = 0.6)) +
    geom_point(size = 3.5, position = position_dodge(width = 0.6)) +
    facet_grid(variable_clean ~ model, scales = "free_y") +
    labs(
      title = "WTP for Expected Richness (Overall)", 
      subtitle = paste0(
        "Point estimates with 95% confidence intervals | Models: ", paste(models, collapse = ", ")
      ),
      x = NULL, 
      y = "WTP (INR)", 
        color = "Scenario"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 15, face = "bold"), 
        plot.subtitle = element_text(size = 11, color = "gray30", margin = margin(b = 15)), 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 9), 
        axis.text.y = element_text(size = 9), 
        strip.text.x = element_text(size = 11, face = "bold"), 
        strip.text.y = element_text(size = 10, face = "bold", angle = 0, hjust = 0), 
        strip.background = element_rect(fill = "gray95", color = "gray80"), 
        panel.grid.minor = element_blank(), 
        panel.spacing.x = unit(1.2, "lines"), 
        panel.spacing.y = unit(1.5, "lines"), 
        legend.position = "bottom", 
        legend.title = element_text(face = "bold", size = 10), 
        legend.text = element_text(size = 9)
      ) +
      scale_color_manual(values = scenario_color_map)

  # Plot biodiversity indices overall
  p_index <- ggplot(wtp_index, aes(x = scenario, y = estimate, color = scenario, group = scenario)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                  width = 0.3, linewidth = 0.9, position = position_dodge(width = 0.6)) +
    geom_point(size = 3.5, position = position_dodge(width = 0.6)) +
    facet_grid(variable_clean ~ model, scales = "free_y") +
    labs(
      title = "WTP for Biodiversity Indices (Overall)", 
      subtitle = paste0(
        "Point estimates with 95% confidence intervals | Models: ", paste(models, collapse = ", ")
      ),
      x = NULL, 
      y = "WTP (INR)", 
      color = "Scenario"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 15, face = "bold"), 
      plot.subtitle = element_text(size = 11, color = "gray30", margin = margin(b = 15)), 
      axis.text.x = element_text(angle = 45, hjust = 1, size = 9), 
      axis.text.y = element_text(size = 9), 
      strip.text.x = element_text(size = 11, face = "bold"), 
      strip.text.y = element_text(size = 10, face = "bold", angle = 0, hjust = 0), 
      strip.background = element_rect(fill = "gray95", color = "gray80"), 
      panel.grid.minor = element_blank(), 
      panel.spacing.x = unit(1.2, "lines"), 
      panel.spacing.y = unit(1.5, "lines"), 
      legend.position = "bottom", 
      legend.title = element_text(face = "bold", size = 10), 
      legend.text = element_text(size = 9)
    ) +
    scale_color_manual(values = scenario_color_map)

  # Plot biodiversity indices seasonal
  p_index_seasonal <- ggplot(wtp_index_seasonal, aes(x = scenario, y = estimate, color = scenario, group = scenario)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                  width = 0.3, linewidth = 0.9, position = position_dodge(width = 0.6)) +
    geom_point(size = 3.5, position = position_dodge(width = 0.6)) +
    facet_grid(variable_clean ~ model, scales = "free_y") +
    labs(
      title = "WTP for Biodiversity Indices (Seasonal)", 
      subtitle = paste0(
        "Point estimates with 95% confidence intervals | Models: ", paste(models, collapse = ", ")
      ),
      x = NULL, 
      y = "WTP (INR)", 
      color = "Scenario"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 15, face = "bold"), 
      plot.subtitle = element_text(size = 11, color = "gray30", margin = margin(b = 15)), 
      axis.text.x = element_text(angle = 45, hjust = 1, size = 9), 
      axis.text.y = element_text(size = 9), 
      strip.text.x = element_text(size = 11, face = "bold"), 
      strip.text.y = element_text(size = 10, face = "bold", angle = 0, hjust = 0), 
      strip.background = element_rect(fill = "gray95", color = "gray80"), 
      panel.grid.minor = element_blank(), 
      panel.spacing.x = unit(1.2, "lines"), 
      panel.spacing.y = unit(1.5, "lines"), 
      legend.position = "bottom", 
      legend.title = element_text(face = "bold", size = 10), 
      legend.text = element_text(size = 9)
    ) +
    scale_color_manual(values = scenario_color_map)

  # Plot ER seasonal
  p_erseason <- ggplot(wtp_erseason, aes(x = scenario, y = estimate, color = scenario, group = scenario)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                  width = 0.3, linewidth = 0.9, position = position_dodge(width = 0.6)) +
    geom_point(size = 3.5, position = position_dodge(width = 0.6)) +
    facet_grid(variable_clean ~ model, scales = "free_y") +
    labs(
      title = "WTP for Expected Richness (Seasonal)", 
      subtitle = paste0(
        "Point estimates with 95% confidence intervals | Models: ", paste(models, collapse = ", ")
      ),
      x = NULL, 
      y = "WTP (INR)", 
      color = "Scenario"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 15, face = "bold"), 
      plot.subtitle = element_text(size = 11, color = "gray30", margin = margin(b = 15)), 
      axis.text.x = element_text(angle = 45, hjust = 1, size = 9), 
      axis.text.y = element_text(size = 9), 
      strip.text.x = element_text(size = 11, face = "bold"), 
      strip.text.y = element_text(size = 10, face = "bold", angle = 0, hjust = 0), 
      strip.background = element_rect(fill = "gray95", color = "gray80"), 
      panel.grid.minor = element_blank(), 
      panel.spacing.x = unit(1.2, "lines"), 
      panel.spacing.y = unit(1.5, "lines"), 
      legend.position = "bottom", 
      legend.title = element_text(face = "bold", size = 10), 
      legend.text = element_text(size = 9)
    ) +
    scale_color_manual(values = scenario_color_map)
}
```


```{r wtp-er-plot}
#| fig-height: !expr if(exists("fig_height_er")) fig_height_er else 20

if (exists("p_er")) {
  print(p_er)
} else {
  cat("No Expected Richness WTP estimates available\n")
}
```


```{r wtp-er-season-plot}
#| fig-height: !expr if(exists("fig_height_er")) fig_height_er else 60

if (exists("p_erseason")) {
  print(p_erseason)
} else {
  cat("No Expected Richness (Seasonal) WTP estimates available\n")
}
```