---
title: "Biodiversity WTP Analysis - Summary Report"
date: "`r Sys.Date()`"
format: 
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    theme: cosmo
    embed-resources: true
    fig-width: 14
    fig-height: 18
params:
  scenarios:
    value:
      - full_c5km_v5km_r50km_mInf
  models:
    value:
      - ER_indxyear-sitexseason_choiceset10
      - ERmigrant_indxyear-sitexseason_choiceset10
  output_dir:
    value: "output/scenarios"
  district_shp:
    value: ""
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(kableExtra)
library(RColorBrewer)
library(htmltools)
library(arrow)
library(data.table)
library(sf)

# Get parameters
scenarios <- params$scenarios
models <- params$models
output_dir <- params$output_dir
district_shp_path <- params$district_shp

message("Scenarios: ", paste(scenarios, collapse = ", "))
message("Models: ", paste(models, collapse = ", "))

# Verify scenario directories exist
for (scenario in scenarios) {
  scenario_dir <- file.path(output_dir, scenario)
  if (!dir.exists(scenario_dir)) {
    warning("Scenario directory not found: ", scenario_dir)
  }
}
```

# Overview

This report summarizes the Random Utility Model (RUM) analysis across **`r length(scenarios)` scenario(s)**: `r paste(scenarios, collapse = ", ")`.

---

# Voronoi Clusters

```{r voronoi-generate}
# Generated directly here rather than by a separate script -- these are
# cheap to (re)draw from the already-computed Voronoi polygons + hotspot
# points, so there's no real benefit to caching a PNG on disk separately.
india_boundary <- NULL
if (nzchar(district_shp_path) && file.exists(district_shp_path)) {
  india_boundary <- st_read(district_shp_path, quiet = TRUE) %>%
    st_union() %>%
    st_transform(crs = 4326)
}

make_voronoi_plot <- function(scenario) {
  voronoi_path <- file.path("data", "intermediate", "scenarios", scenario, "ebird_hotspots_voronoi.gpkg")
  hotspots_path <- file.path("data", "intermediate", "scenarios", scenario, "ebird_hotspots_clustered.parquet")

  if (!file.exists(voronoi_path) || !file.exists(hotspots_path)) {
    return(NULL)
  }

  voronoi_limited <- st_read(voronoi_path, layer = "cluster_voronoi_limited", quiet = TRUE)
  hotspots <- read_parquet(hotspots_path)

  p <- ggplot()
  if (!is.null(india_boundary)) {
    p <- p + geom_sf(data = india_boundary, fill = NA, color = "gray30", linewidth = 0.8)
  }
  p <- p +
    geom_sf(data = st_transform(voronoi_limited, 4326),
            fill = "lightblue", alpha = 0.3, color = "blue", linewidth = 0.3) +
    geom_point(data = hotspots, aes(x = lon, y = lat),
               color = "red", size = 0.8, alpha = 0.6) +
    labs(
      title = "Voronoi Clusters and Hotspot Locations",
      subtitle = paste0("Scenario: ", scenario, " | ",
                         nrow(voronoi_limited), " clusters, ", nrow(hotspots), " hotspots"),
      x = "Longitude", y = "Latitude"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 10),
      panel.grid.minor = element_blank()
    )
  p
}
```

:::{.panel-tabset}

```{r voronoi-tabs, results='asis', fig.width=10, fig.height=12}
for (scenario in scenarios) {
  cat('\n##', scenario, '\n\n')
  p <- make_voronoi_plot(scenario)
  if (is.null(p)) {
    cat("Voronoi data not found for scenario:", scenario, "\n\n")
  } else {
    print(p)
    cat("\n\n")
  }
}
```

:::

---

# Data Summary

```{r load-scenario-data}
# Loaded ONCE per scenario here, reused by both the Data Summary table below
# and the biodiversity histogram section further down -- avoids reading the
# same multi-GB model_data parquet twice. Sourced from model_data_{scenario}
# (the actual post-11a data used for estimation, filtered/cleaned), NOT the
# pre-cleaning master_data_with_travel_cost file -- fixes a prior mismatch
# where this report's summary stats described a different, larger sample
# than what was actually estimated.
#
# Columns are pushed down via arrow's Dataset API rather than reading the
# full wide table -- model_data has dozens of columns and can be tens of
# millions of rows, so being selective here matters for memory.

summary_vars <- c(
  "expected_richness", "migrant_richness", "resident_richness",
  "species_richness", "shannon_index", "simpson_index",
  "expected_richness_Winter", "expected_richness_Spring", "expected_richness_Summer",
  "migrant_richness_Winter", "migrant_richness_Spring", "migrant_richness_Summer",
  "resident_richness_Winter", "resident_richness_Spring", "resident_richness_Summer",
  "expected_congestion", "precip", "temp", "trees",
  "travel_cost_combined", "dist_to_pa_km", "geo_dist", "choice_set_size"
)
# Note: no "_Fall" variants -- Fall is the omitted reference season and is
# never materialized as its own column (Winter/Spring/Summer are relative to
# it). species_richness/shannon_index/simpson_index also have no seasonal
# split anywhere in the pipeline, unlike the three richness measures above.

needed_cols <- c("trip_id", "user_id", "choice", "year", summary_vars)

scenario_summaries <- list()
scenario_histograms <- list()

for (scenario in scenarios) {
  model_data_path <- file.path("output", "models", paste0("model_data_", scenario, ".parquet"))
  if (!file.exists(model_data_path)) {
    message("model_data not found for scenario: ", scenario, " (", model_data_path, ")")
    next
  }

  ds <- arrow::open_dataset(model_data_path)
  available_cols <- intersect(needed_cols, names(ds))
  md <- ds %>% dplyr::select(dplyr::all_of(available_cols)) %>% dplyr::collect()
  setDT(md)

  # --- Summary stats for this scenario ---
  avail_summary_vars <- intersect(summary_vars, names(md))
  stats <- md[, lapply(.SD, function(x) {
    list(mean = mean(x, na.rm = TRUE), sd = sd(x, na.rm = TRUE),
         min = min(x, na.rm = TRUE), median = median(x, na.rm = TRUE),
         max = max(x, na.rm = TRUE), n_missing = sum(is.na(x)),
         pct_missing = 100 * sum(is.na(x)) / length(x))
  }), .SDcols = avail_summary_vars]

  long_df <- data.frame(
    variable = rep(names(stats), each = 7),
    statistic = rep(c("mean", "sd", "min", "median", "max", "n_missing", "pct_missing"), length(stats)),
    value = unlist(stats)
  )
  wide_df <- long_df %>% pivot_wider(names_from = statistic, values_from = value)

  scenario_summaries[[scenario]] <- rbind(
    data.frame(variable = "Sample Size", mean = nrow(md), sd = NA, min = NA, median = NA, max = NA, n_missing = NA, pct_missing = NA),
    data.frame(variable = "Number of Trips", mean = md[, uniqueN(trip_id)], sd = NA, min = NA, median = NA, max = NA, n_missing = NA, pct_missing = NA),
    data.frame(variable = "Number of Users", mean = md[, uniqueN(user_id)], sd = NA, min = NA, median = NA, max = NA, n_missing = NA, pct_missing = NA),
    data.frame(variable = "Year Range", mean = NA, sd = NA,
               min = md[, min(year, na.rm = TRUE)], median = NA,
               max = md[, max(year, na.rm = TRUE)], n_missing = NA, pct_missing = NA),
    data.frame(variable = "Number of Years", mean = md[, uniqueN(year)], sd = NA, min = NA, median = NA, max = NA, n_missing = NA, pct_missing = NA),
    wide_df
  )

  # --- Distilled data for the biodiversity histogram (choice + 3 richness vars only) ---
  hist_cols <- intersect(c("choice", "expected_richness", "migrant_richness", "resident_richness"), names(md))
  scenario_histograms[[scenario]] <- md[, ..hist_cols]

  rm(md)
  gc()
}
```

```{r data-summary-combined}
key_vars <- c(
  "Sample Size", "Number of Trips", "Number of Users", "Year Range", "Number of Years",
  "expected_richness", "migrant_richness", "resident_richness",
  "shannon_index", "simpson_index",
  "expected_richness_Winter", "expected_richness_Spring", "expected_richness_Summer",
  "migrant_richness_Winter", "migrant_richness_Spring", "migrant_richness_Summer",
  "resident_richness_Winter", "resident_richness_Spring", "resident_richness_Summer",
  "expected_congestion", "precip", "temp", "trees",
  "travel_cost_combined", "travel_cost_min", "travel_cost_median", "travel_cost_max",
  "dist_to_pa_km", "geo_dist", "choice_set_size"
)

summary_list <- list()
for (scenario in names(scenario_summaries)) {
  df <- scenario_summaries[[scenario]]

  # Pull out extra min/median/max detail rows for travel cost specifically --
  # this is the price variable underlying every WTP estimate, so its full
  # range matters more here than for other variables (where mean (SD) alone
  # is enough for a presentation table)
  tc_row <- df %>% filter(variable == "travel_cost_combined")
  tc_detail <- if (nrow(tc_row) == 1) {
    data.frame(
      variable = c("travel_cost_min", "travel_cost_median", "travel_cost_max"),
      mean = c(tc_row$min, tc_row$median, tc_row$max),
      sd = NA
    )
  } else {
    data.frame(variable = character(0), mean = numeric(0), sd = numeric(0))
  }

  df_filtered <- df %>%
    filter(variable %in% key_vars) %>%
    select(variable, mean, sd) %>%
    bind_rows(tc_detail) %>%
    mutate(
      formatted = case_when(
        variable == "Year Range" ~ paste0(df$min[df$variable == "Year Range"], "-", df$max[df$variable == "Year Range"]),
        variable %in% c("Sample Size", "Number of Trips", "Number of Users", "Number of Years") ~
          format(round(mean, 0), big.mark = ",", scientific = FALSE),
        TRUE ~ paste0(format(round(mean, 2), nsmall = 2),
                       ifelse(!is.na(sd) & sd > 0, paste0(" (", format(round(sd, 2), nsmall = 2), ")"), ""))
      )
    )
  summary_list[[scenario]] <- df_filtered %>% select(variable, formatted)
  names(summary_list[[scenario]])[2] <- scenario
}

if (length(summary_list) > 0) {
  summary_combined <- Reduce(function(x, y) full_join(x, y, by = "variable"), summary_list)

  summary_combined <- summary_combined %>%
    mutate(variable = factor(variable, levels = key_vars)) %>%
    arrange(variable) %>%
    filter(!is.na(variable)) %>%
    mutate(variable = as.character(variable))

  var_labels <- c(
    "Sample Size" = "Sample Size", "Number of Trips" = "Number of Trips", "Number of Users" = "Number of Users",
    "Year Range" = "Year Range", "Number of Years" = "Number of Years",
    "expected_richness" = "Expected Richness", "migrant_richness" = "Migrant Richness", "resident_richness" = "Resident Richness",
    "shannon_index" = "Shannon Index", "simpson_index" = "Simpson Index",
    "expected_richness_Winter" = "Expected Richness (Winter)", "expected_richness_Spring" = "Expected Richness (Spring)", "expected_richness_Summer" = "Expected Richness (Summer)",
    "migrant_richness_Winter" = "Migrant Richness (Winter)", "migrant_richness_Spring" = "Migrant Richness (Spring)", "migrant_richness_Summer" = "Migrant Richness (Summer)",
    "resident_richness_Winter" = "Resident Richness (Winter)", "resident_richness_Spring" = "Resident Richness (Spring)", "resident_richness_Summer" = "Resident Richness (Summer)",
    "expected_congestion" = "Expected Congestion", "precip" = "Precipitation (mm)", "temp" = "Temperature (°C)", "trees" = "Tree Cover (%)",
    "travel_cost_combined" = "Travel Cost (INR, mean)", "travel_cost_min" = "Travel Cost (INR, min)",
    "travel_cost_median" = "Travel Cost (INR, median)", "travel_cost_max" = "Travel Cost (INR, max)",
    "dist_to_pa_km" = "Distance to PA (km)", "geo_dist" = "Distance to Site (km)",
    "choice_set_size" = "Choice Set Size"
  )

  summary_combined <- summary_combined %>%
    mutate(Variable = ifelse(variable %in% names(var_labels), var_labels[variable], variable)) %>%
    select(-variable) %>%
    select(Variable, everything())

  kable(summary_combined,
        align = c("l", rep("r", length(scenarios))),
        caption = "Summary Statistics Across Scenarios (Mean with SD in parentheses, unless noted otherwise) -- computed from the post-cleaning model_data used for estimation") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    row_spec(0, bold = TRUE) %>%
    row_spec(1:3, background = "#f0f0f0")
} else {
  cat("No summary data available")
}
```

---

# Biodiversity Distribution Across Choice Sets

Distributions use the full candidate choice sets (before down-sampling to
the fixed alternative-set size used for estimation) -- "Available" is every
alternative a person could have chosen from; "Chosen" is the site they
actually visited. Densities (not raw counts) are shown so the two groups'
*shapes* are comparable despite very different sample sizes.

:::{.panel-tabset}

```{r biodiversity-histograms, results='asis', fig.width=10, fig.height=12}
metric_labels <- c(
  expected_richness = "Expected Richness",
  migrant_richness = "Migrant Richness",
  resident_richness = "Resident Richness"
)

for (scenario in scenarios) {
  cat('\n##', scenario, '\n\n')

  hd <- scenario_histograms[[scenario]]
  if (is.null(hd) || nrow(hd) == 0) {
    cat("No choice-set data available for scenario:", scenario, "\n\n")
    next
  }

  metrics_present <- intersect(names(metric_labels), names(hd))
  long_rows <- list()
  for (m in metrics_present) {
    vals <- hd[[m]]
    long_rows[[paste0(m, "_avail")]] <- data.frame(value = vals, group = "Available", metric = metric_labels[[m]])
    chosen_vals <- vals[hd$choice == 1]
    long_rows[[paste0(m, "_chosen")]] <- data.frame(value = chosen_vals, group = "Chosen", metric = metric_labels[[m]])
  }
  long_data <- do.call(rbind, long_rows)
  long_data <- long_data[!is.na(long_data$value), ]
  long_data$metric <- factor(long_data$metric, levels = unname(metric_labels))
  long_data$group <- factor(long_data$group, levels = c("Available", "Chosen"))

  p <- ggplot(long_data, aes(x = value, fill = group)) +
    geom_histogram(aes(y = after_stat(density)), position = "identity", alpha = 0.5, bins = 30, color = NA) +
    facet_wrap(~metric, scales = "free", ncol = 1) +
    scale_fill_manual(values = c("Available" = "gray50", "Chosen" = "#E41A1C")) +
    labs(
      title = "Biodiversity Distribution: Chosen Sites vs. Available Alternatives",
      subtitle = paste0("Scenario: ", scenario, " | full candidate choice sets (pre-sampling)"),
      x = "Value", y = "Density", fill = ""
    ) +
    theme_minimal() +
    theme(legend.position = "top", strip.text = element_text(face = "bold"))

  print(p)
  cat("\n\n")
}
```

:::

---

# Definitions

::: {.callout-note collapse=true}
## Species Richness Measures

**Expected Species Richness** is computed as the mean number of unique
species observed across all checklists recorded at a site within a given
time period. If expected richness cannot be computed directly for a group
or time period, the pipeline uses the following fallback:

1. If the previous week value is available, use that.
2. If not, use the previous month value.
3. If not, use the previous year-season value.
4. If none are available, the value is marked as missing.

**Migrant Richness** and **Resident Richness** are computed analogously,
restricted to species classified as migratory or resident, respectively.
:::

::: {.callout-note collapse=true}
## Diversity Indices

Diversity indices are computed at the checklist (trip) level using recorded
observation counts. For checklists where counts were not recorded (entered
as "X" in eBird), indices are set to missing. Unlike the richness measures
above, no fallback imputation is applied.

**Shannon Index ($H$):**

The Shannon diversity index quantifies the entropy (uncertainty) in species composition:

$$
H = -\sum_{i=1}^S p_i \log p_i
$$

where $S$ is the number of species detected and 
$p_i = \frac{n_i}{\sum_{j=1}^S n_j}$ is the proportion of total observed individuals belonging to species $i$, based on recorded observation counts. Higher values indicate greater diversity and evenness across species.

**Gini-Simpson Index ($D$):**

The Gini-Simpson index measures the probability that two randomly selected 
individuals belong to *different* species:

$$
D = 1 - \sum_{i=1}^S p_i^2
$$

where $S$ is the number of species detected and 
$p_i = \frac{n_i}{\sum_{j=1}^S n_j}$ is the proportion of total observed  individuals belonging to species $i$, based on recorded observation counts.  Values range from 0 (no diversity) to 1 (maximum diversity).
:::

---

# Willingness to Pay Estimates

```{r wtp-data-prep}
# File pattern: {model}_Mixed_{scenario}_wtp.csv in output/models/
wtp_list <- list()
wtp_files <- list.files("output/models", pattern = "_Mixed_.*_wtp\\.csv$", full.names = TRUE)

if (length(wtp_files) > 0) {
  for (wtp_path in wtp_files) {
    tryCatch({
      filename <- basename(wtp_path)
      temp <- sub("_wtp\\.csv$", "", filename)
      parts <- strsplit(temp, "_Mixed_")[[1]]

      if (length(parts) == 2) {
        model_name <- parts[1]
        scenario_name <- parts[2]

        wtp_df <- read.csv(wtp_path, stringsAsFactors = FALSE) %>%
          rename(variable = Variable, estimate = WTP, se = Std.Err,
                 scenario = Scenario, model = Model) %>%
          select(variable, estimate, se, scenario, model)

        wtp_list[[paste(scenario_name, model_name, sep = "_")]] <- wtp_df
      }
    }, error = function(e) {
      cat("\n[WARNING] Failed to load WTP from:", basename(wtp_path), "-", conditionMessage(e), "\n")
    })
  }
} else {
  cat("\n[WARNING] No WTP CSV files found in output/models/\n")
}

wtp_combined <- if (length(wtp_list) > 0) {
  bind_rows(wtp_list) %>%
    mutate(variable = gsub("_dm$", "", variable),
           ci_lower = estimate - 1.96 * se,
           ci_upper = estimate + 1.96 * se)
} else {
  NULL
}
```

```{r wtp-prepare-plots}
model_plots <- list()

if (!is.null(wtp_combined)) {
  desired_order <- c(
    "expected_richness (Overall)", "expected_richness (Winter)", "expected_richness (Spring)", "expected_richness (Summer)",
    "migrant_richness (Overall)", "migrant_richness (Winter)", "migrant_richness (Spring)", "migrant_richness (Summer)",
    "resident_richness (Overall)", "resident_richness (Winter)", "resident_richness (Spring)", "resident_richness (Summer)"
  )

  for (curr_model in unique(wtp_combined$model)) {
    model_data <- wtp_combined %>%
      filter(model == curr_model) %>%
      mutate(
        variable_clean = case_when(
          grepl("Winter", variable) ~ paste(sub("_Winter", "", variable), "(Winter)"),
          grepl("Spring", variable) ~ paste(sub("_Spring", "", variable), "(Spring)"),
          grepl("Summer", variable) ~ paste(sub("_Summer", "", variable), "(Summer)"),
          TRUE ~ paste(variable, "(Overall)")
        )
      ) %>%
      filter(variable_clean %in% desired_order) %>%
      mutate(variable_clean = factor(variable_clean, levels = desired_order))

    if (nrow(model_data) > 0) {
      model_plots[[curr_model]] <- model_data
    }
  }
}
```

```{r wtp-plot-build}
model_plots_list <- list()

if (!is.null(wtp_combined) && length(model_plots) > 0) {
  scenario_names <- unique(wtp_combined$scenario)
  n_scenarios <- length(scenario_names)
  palette <- if (n_scenarios <= 8) {
    RColorBrewer::brewer.pal(max(n_scenarios, 3), "Set1")[1:n_scenarios]
  } else {
    colorRampPalette(RColorBrewer::brewer.pal(8, "Set1"))(n_scenarios)
  }
  scenario_color_map <- setNames(palette, scenario_names)

  for (curr_model in names(model_plots)) {
    model_data <- model_plots[[curr_model]] %>%
      mutate(variable_clean = factor(variable_clean, levels = unique(variable_clean)))

    p <- ggplot(model_data, aes(x = variable_clean, y = estimate, color = scenario, group = scenario)) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
      geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, linewidth = 0.8, position = position_dodge(width = 0.6)) +
      geom_point(size = 3, position = position_dodge(width = 0.6)) +
      labs(
        title = paste0("WTP - ", gsub("_", " ", curr_model)),
        subtitle = "Point estimates with 95% confidence intervals",
        x = "Variables", y = "WTP (INR)", color = "Scenario"
      ) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      scale_color_manual(values = scenario_color_map)

    model_plots_list[[curr_model]] <- p
  }
}
```

```{r wtp-model-plots}
#| fig-height: !expr if(exists("model_plots_list") && length(model_plots_list) > 0) 8 else 2
#| results: asis

if (exists("model_plots_list") && length(model_plots_list) > 0) {
  for (model_name in names(model_plots_list)) {
    cat("\n### ", gsub("_", " ", model_name), " {.unnumbered}\n\n")
    print(model_plots_list[[model_name]])
    cat("\n\n")
  }
} else {
  cat("No WTP estimates available\n")
}
```
