---
title: "Biodiversity WTP Analysis - Summary Report"
date: "`r Sys.Date()`"
format: 
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    theme: cosmo
    embed-resources: true
    fig-width: 14
    fig-height: 18
params:
  scenarios:
    value:
      - baseline
  models:
    value:
      - Basic
  output_dir:
    value: "output/scenarios"
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(kableExtra)
library(RColorBrewer)
library(htmltools)

# Get parameters
scenarios <- params$scenarios
models <- params$models
output_dir <- params$output_dir

message("Scenarios: ", paste(scenarios, collapse = ", "))
message("Models: ", paste(models, collapse = ", "))
message("Output directory: ", output_dir)

# Verify scenario directories exist
for (scenario in scenarios) {
  scenario_dir <- file.path(output_dir, scenario)
  if (!dir.exists(scenario_dir)) {
    warning("Scenario directory not found: ", scenario_dir)
  }
}
```

# Overview

This report summarizes the Random Utility Model (RUM) analysis across **`r length(scenarios)` scenarios**: `r paste(scenarios, collapse = ", ")`.

---

# Voronoi Clusters

:::{.panel-tabset}

```{r voronoi-tabs, results='asis'}
for (scenario in scenarios) {
  voronoi_file <- file.path("output", "figures", paste0("voronoi_map_", scenario, ".png"))
  cat('\n##', scenario, '\n\n')
  if (!file.exists(voronoi_file)) {
    cat("Voronoi map not found for scenario:", scenario, "\n\n")
  } else {
    cat('![](', voronoi_file, '){ width=100% }\n\n', sep = '')
  }
}
```

:::

---

# Data Summary

```{r data-summary-combined}
# Load data_summary.csv for each scenario
summary_list <- list()
for (scenario in scenarios) {
  summary_path <- file.path("output", "tables", paste0("data_summary_", scenario, ".csv"))
  if (file.exists(summary_path)) {
    df <- read.csv(summary_path, stringsAsFactors = FALSE)
    # Add all variables used in WTP plots to the summary
    wtp_plot_vars <- c(
      "expected_richness", "migrant_richness", "resident_richness", "species_richness", "shannon_index", "simpson_index",
      "expected_richness_Winter", "expected_richness_Spring", "expected_richness_Summer", "expected_richness_Fall",
      "migrant_richness_Winter", "migrant_richness_Spring", "migrant_richness_Summer", "migrant_richness_Fall",
      "resident_richness_Winter", "resident_richness_Spring", "resident_richness_Summer", "resident_richness_Fall",
      "species_richness_Winter", "species_richness_Spring", "species_richness_Summer", "species_richness_Fall",
      "shannon_index_Winter", "shannon_index_Spring", "shannon_index_Summer", "shannon_index_Fall",
      "simpson_index_Winter", "simpson_index_Spring", "simpson_index_Summer", "simpson_index_Fall"
    )
        key_vars <- c("Sample Size", "Number of Trips", "Number of Users",
          wtp_plot_vars,
          "expected_congestion", "precip", 
          "temp", "trees", "travel_cost_combined", "dist_to_pa_km",
          "distance_to_site", "geo_dist", "choice_set_size")
    found_vars <- intersect(key_vars, df$variable)
    df_filtered <- df %>%
      filter(variable %in% key_vars) %>%
      select(variable, mean, sd)
    df_filtered <- df_filtered %>%
      mutate(
        formatted = ifelse(
          variable %in% c("Sample Size", "Number of Trips", "Number of Users"),
          format(round(mean, 0), big.mark = ",", scientific = FALSE),
          paste0(
            format(round(mean, 2), nsmall = 2),
            ifelse(!is.na(sd) & sd > 0, 
                   paste0(" (", format(round(sd, 2), nsmall = 2), ")"),
                   "")
          )
        )
      )
    summary_list[[scenario]] <- df_filtered %>%
      select(variable, formatted)
    names(summary_list[[scenario]])[2] <- scenario
  } else {
    cat("[DataSummary] NOT FOUND: ", summary_path)
  }
}

# Merge all scenarios
if (length(summary_list) > 0) {
  summary_combined <- Reduce(function(x, y) {
    full_join(x, y, by = "variable")
  }, summary_list)
  
  # Reorder rows
  var_order <- c(
    "Sample Size", "Number of Trips", "Number of Users",
    "expected_richness", "migrant_richness", "resident_richness", "shannon_index",  "simpson_index",
    "expected_richness_Winter", "expected_richness_Spring",   "expected_richness_Summer", "expected_richness_Fall",
    "migrant_richness_Winter", "migrant_richness_Spring", "migrant_richness_Summer",  "migrant_richness_Fall",
    "resident_richness_Winter", "resident_richness_Spring",   "resident_richness_Summer", "resident_richness_Fall",
    "shannon_index_Winter", "shannon_index_Spring", "shannon_index_Summer",   "shannon_index_Fall",
    "simpson_index_Winter", "simpson_index_Spring", "simpson_index_Summer",   "simpson_index_Fall",
    "expected_congestion", "precip", "temp", "trees", "travel_cost_combined",   "dist_to_pa_km",
    "distance_to_site", "geo_dist", "choice_set_size"
  )
  
  summary_combined <- summary_combined %>%
    mutate(variable = factor(variable, levels = var_order)) %>%
    arrange(variable) %>%
    filter(!is.na(variable)) %>%   # drop anything not in var_order
    mutate(variable = as.character(variable))
  
  # Clean variable names for display
  summary_combined <- summary_combined %>%
    mutate(
      Variable = case_when(
        variable == "Sample Size" ~ "Sample Size",
        variable == "Number of Trips" ~ "Number of Trips",
        variable == "Number of Users" ~ "Number of Users",
        variable == "expected_richness" ~ "Expected Richness",
        variable == "expected_congestion" ~ "Expected Congestion",
        variable == "precip" ~ "Precipitation (mm)",
        variable == "temp" ~ "Temperature (°C)",
        variable == "trees" ~ "Tree Cover (%)",
        variable == "travel_cost_combined" ~ "Travel Cost (INR)",
        variable == "dist_to_pa_km" ~ "Distance to PA (km)",
        variable %in% c("distance_to_site", "geo_dist") ~ "Distance to Site (km)",
        variable == "choice_set_size" ~ "Choice Set Size",
          variable == "migrant_richness" ~ "Migrant Richness",
          variable == "resident_richness" ~ "Resident Richness",
          variable == "species_richness" ~ "Species Richness",
          variable == "shannon_index" ~ "Shannon Index",
          variable == "simpson_index" ~ "Simpson Index",
          variable == "expected_richness_Winter" ~ "Expected Richness (Winter)",
          variable == "expected_richness_Spring" ~ "Expected Richness (Spring)",
          variable == "expected_richness_Summer" ~ "Expected Richness (Summer)",
          variable == "expected_richness_Fall" ~ "Expected Richness (Fall)",
          variable == "migrant_richness_Winter" ~ "Migrant Richness (Winter)",
          variable == "migrant_richness_Spring" ~ "Migrant Richness (Spring)",
          variable == "migrant_richness_Summer" ~ "Migrant Richness (Summer)",
          variable == "migrant_richness_Fall" ~ "Migrant Richness (Fall)",
          variable == "resident_richness_Winter" ~ "Resident Richness (Winter)",
          variable == "resident_richness_Spring" ~ "Resident Richness (Spring)",
          variable == "resident_richness_Summer" ~ "Resident Richness (Summer)",
          variable == "resident_richness_Fall" ~ "Resident Richness (Fall)",
          variable == "species_richness_Winter" ~ "Species Richness (Winter)",
          variable == "species_richness_Spring" ~ "Species Richness (Spring)",
          variable == "species_richness_Summer" ~ "Species Richness (Summer)",
          variable == "species_richness_Fall" ~ "Species Richness (Fall)",
          variable == "shannon_index_Winter" ~ "Shannon Index (Winter)",
          variable == "shannon_index_Spring" ~ "Shannon Index (Spring)",
          variable == "shannon_index_Summer" ~ "Shannon Index (Summer)",
          variable == "shannon_index_Fall" ~ "Shannon Index (Fall)",
          variable == "simpson_index_Winter" ~ "Simpson Index (Winter)",
          variable == "simpson_index_Spring" ~ "Simpson Index (Spring)",
          variable == "simpson_index_Summer" ~ "Simpson Index (Summer)",
          variable == "simpson_index_Fall" ~ "Simpson Index (Fall)",
        TRUE ~ variable
      )
    ) %>%
    select(-variable) %>%
    select(Variable, everything())
  
  kable(summary_combined,
        align = c("l", rep("r", length(scenarios))),
        caption = "Summary Statistics Across Scenarios (Mean with SD in parentheses)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE) %>%
    row_spec(0, bold = TRUE) %>%
    row_spec(1:3, background = "#f0f0f0")
} else {
  cat("No summary data available")
}
```

# Definitions

### Species Richness Measures

**Expected Species Richness** is computed as the mean number of unique species 
observed across all checklists recorded at a site within a given time period. 
If expected richness cannot be computed directly for a group or time period, 
the pipeline uses the following fallback:

- If the previous week value is available, use that.
- If not, use the previous month value.
- If not, use the previous year-season value.
- If none are available, the value is marked as missing.

**Migrant Richness** and **Resident Richness** are computed analogously, 
restricted to species classified as migratory or resident, respectively.

### Diversity Indices

Diversity indices are computed at the checklist (trip) level using recorded observation counts. For checklists where counts were not recorded (entered as "X" in eBird), indices are set to missing. Unlike the richness measures above, no fallback imputation is applied.

**Shannon Index ($H$):**

The Shannon diversity index quantifies the entropy (uncertainty) in species composition:

$$
H = -\sum_{i=1}^S p_i \log p_i
$$

where $S$ is the number of species detected and 
$p_i = \frac{n_i}{\sum_{j=1}^S n_j}$ is the proportion of total observed individuals belonging to species $i$, based on recorded observation counts. Higher values indicate greater diversity and evenness across species.

**Gini-Simpson Index ($D$):**

The Gini-Simpson index measures the probability that two randomly selected 
individuals belong to *different* species:

$$
D = 1 - \sum_{i=1}^S p_i^2
$$

where $S$ is the number of species detected and 
$p_i = \frac{n_i}{\sum_{j=1}^S n_j}$ is the proportion of total observed  individuals belonging to species $i$, based on recorded observation counts.  Values range from 0 (no diversity) to 1 (maximum diversity).

---

# Willingness to Pay Estimates

```{r wtp-data-prep, echo=FALSE, message=FALSE}
# Load WTP data from CSV files created by 11b stage
# File pattern: {model}_Mixed_{scenario}_wtp.csv in output/models/

wtp_list <- list()
models <- c()

# List all WTP CSV files
wtp_files <- list.files("output/models", pattern = "_Mixed_.*_wtp\\.csv$", full.names = TRUE)

if (length(wtp_files) > 0) {
  for (wtp_path in wtp_files) {
    tryCatch({
      # Extract model and scenario from filename using base R regex
      # Pattern: {model}_Mixed_{scenario}_wtp.csv
      filename <- basename(wtp_path)
      
      # Use sub() to extract parts
      # First, remove the trailing _wtp.csv
      temp <- sub("_wtp\\.csv$", "", filename)
      
      # Split on _Mixed_ to get model and scenario
      parts <- strsplit(temp, "_Mixed_")[[1]]
      
      if (length(parts) == 2) {
        model_name <- parts[1]
        scenario_name <- parts[2]
        
        # Add to models list
        models <- c(models, model_name)
        
        # Read WTP CSV
        wtp_df <- read.csv(wtp_path, stringsAsFactors = FALSE)
        
        # Rename columns to match expected format
        wtp_df <- wtp_df %>%
          rename(
            variable = Variable,
            estimate = WTP,
            se = Std.Err,
            scenario = Scenario,
            model = Model
          ) %>%
          select(variable, estimate, se, scenario, model)
        
        # Store in list
        wtp_list[[paste(scenario_name, model_name, sep = "_")]] <- wtp_df
      }
    }, error = function(e) {
      cat("\n[WARNING] Failed to load WTP from:", basename(wtp_path), "\n")
      cat("Error:", conditionMessage(e), "\n")
    })
  }
} else {
  cat("\n[WARNING] No WTP CSV files found in output/models/\n")
}
```

```{r wtp-prepare-plots}
if (length(wtp_list) > 0) {
  wtp_combined <- bind_rows(wtp_list)
  wtp_combined <- wtp_combined %>% mutate(variable = gsub("_dm$", "", variable))
  wtp_combined <- wtp_combined %>% mutate(
    ci_lower = estimate - 1.96 * se,
    ci_upper = estimate + 1.96 * se
  )

  # Get unique models and prepare grouped data
  unique_models <- unique(wtp_combined$model)
  
  # Create list to store plots
  model_plots <- list()
  
  # For each model, combine ALL its variables (overall + seasonal)
  for (curr_model in unique_models) {
    # model_data <- wtp_combined %>% 
    #   filter(model == curr_model) %>%
    #   mutate(
    #     variable_clean = case_when(
    #       grepl("Winter", variable) ~ paste(sub("_Winter", "", variable), "(Winter)"),
    #       grepl("Spring", variable) ~ paste(sub("_Spring", "", variable), "(Spring)"),
    #       grepl("Summer", variable) ~ paste(sub("_Summer", "", variable), "(Summer)"),
    #       grepl("Fall", variable) ~ paste(sub("_Fall", "", variable), "(Fall)"),
    #       TRUE ~ paste(variable, "(Overall)")
    #     )
    #   )
    model_data <- wtp_combined %>% 
      filter(model == curr_model) %>%
      mutate(
        variable_clean = case_when(
          grepl("Winter", variable) ~ paste(sub   ("_Winter", "", variable), "(Winter)"),
          grepl("Spring", variable) ~ paste(sub   ("_Spring", "", variable), "(Spring)"),
          grepl("Summer", variable) ~ paste(sub   ("_Summer", "", variable), "(Summer)"),
          grepl("Fall", variable) ~ paste(sub("_Fall",    "", variable), "(Fall)"),
          TRUE ~ paste(variable, "(Overall)")
        )
      )

    # ---- SELECT + ORDER VARIABLES ----
    desired_order <- c(
      # Expected richness
      "expected_richness (Overall)",
      "expected_richness (Winter)",
      "expected_richness (Spring)",
      "expected_richness (Summer)",
      
      # Migrant richness
      "migrant_richness (Overall)",
      "migrant_richness (Winter)",
      "migrant_richness (Spring)",
      "migrant_richness (Summer)",
      
      # Resident richness
      "resident_richness (Overall)",
      "resident_richness (Winter)",
      "resident_richness (Spring)",
      "resident_richness (Summer)"
    )
    
    model_data <- model_data %>%
      filter(variable_clean %in% desired_order) %>%   # keep only these
      mutate(variable_clean = factor(variable_clean, levels = desired_order))
    
    if (nrow(model_data) > 0) {
      model_plots[[curr_model]] <- model_data
    }
  }
} else {
  cat("\n[WARNING] No WTP data found\n")
  model_plots <- list()
}
```

```{r wtp-plot-build}
# Color map
scenario_names <- unique(wtp_combined$scenario)
n_scenarios <- length(scenario_names)

if (n_scenarios <= 8) {
  palette <- RColorBrewer::brewer.pal(n_scenarios, "Set1")
} else {
  palette <- colorRampPalette(RColorBrewer::brewer.pal(8, "Set1"))(n_scenarios)
}

scenario_color_map <- setNames(palette, scenario_names)

# Create ONE plot per model with ALL variables together
model_plots_list <- list()

for (curr_model in unique(wtp_combined$model)) {
  model_data <- model_plots[[curr_model]] %>%
    mutate(variable_clean = factor(variable_clean, levels = unique(variable_clean)))

  if (nrow(model_data) > 0) {
    p <- ggplot(model_data, aes(x = variable_clean, y = estimate, color = scenario, group = scenario)) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
      geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                    width = 0.2, linewidth = 0.8,
                    position = position_dodge(width = 0.6)) +
      geom_point(size = 3, position = position_dodge(width = 0.6)) +
      labs(
        title = paste0("WTP - ", gsub("_", " ", curr_model)),
        subtitle = "Point estimates with 95% confidence intervals",
        x = "Variables",
        y = "WTP (INR)",
        color = "Scenario"
      ) +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1)
      ) +
      scale_color_manual(values = scenario_color_map)

    model_plots_list[[curr_model]] <- p
  }
}
```

```{r wtp-model-plots}
#| fig-height: !expr if(exists("model_plots_list") && length(model_plots_list) > 0) 8 else 2
#| results: asis

if (exists("model_plots_list") && length(model_plots_list) > 0) {
  for (model_name in names(model_plots_list)) {
    cat("\n### ", gsub("_", " ", model_name), " {.unnumbered}\n\n")
    print(model_plots_list[[model_name]])
    cat("\n\n")
  }
} else {
  cat("No WTP estimates available\n")
}
```